Clustering of Last.fm Music

### 2015-05-06 writeup/MSDgroupwriteup.tex
correct MAP values

\section{Data Munging}

@@

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=4in]{h845BuzFO9CNgAAAABJRU5ErkJggg==.png} 
   \caption{how close our prediction is as compared to the actual normalized play count in the testing set }
   \label{fig:rmseplot}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=4in]{C9LAAAAABJRU5ErkJggg==.png} 
   \caption{log joint likelihood of the training set as a function of iteration }
   \label{fig:likeplot}
\end{figure}

@@

\subsection{User based and Item based}

\subsection{Using Tags}

\section{Results}

>>>>

\section{Data Munging}
\subsection{Data}
\subsubsection{Data Statistics}
\subsubsection{Problems and Solutions}
\subsection{Normalization}

@@

%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
%   \centering
%   \includegraphics[width=4in]{h845BuzFO9CNgAAAABJRU5ErkJggg==.png} 
%   \caption{how close our prediction is as compared to the actual normalized play count in the testing set }
%   \label{fig:rmseplot}
%\end{figure}
%
%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
%   \centering
%   \includegraphics[width=4in]{C9LAAAAABJRU5ErkJggg==.png} 
%   \caption{log joint likelihood of the training set as a function of iteration }
%   \label{fig:likeplot}
%\end{figure}

@@

\subsection{User Based and Item Based Recommendation}

\subsection{Artist Based Recommendation}

\section{Results}
\subsection{Matrix Factorization}

\subsection{User Based and Item Based Recommendation}

\subsection{Artist Based Recommendation}
